---
title: 'LawnProject Panel Data Analysis / Random Forest Data'
author: 'LawnProject Team'
geometry: margin=1in
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  toc: yes
  number_sections: yes
fontsize: 11pt
header-includes:
  - \usepackage{makecell}
---

Intro

```{r, echo=FALSE, warning=FALSE, message=FALSE}
rm(list = ls())

library(dplyr)
library(tidyverse)
library(magrittr)
library(ggplot2)
library(plm)
library(lattice)
library(patchwork)
library(lubridate)
library(ExPanDaR)
library(stats)
library(car)
library(xts)
library(stargazer)
library(data.table)
library(GGally)
library(knitr)
library(kableExtra)
library(tinytex)
library(data.table)
library(DBI)
library(odbc)
library(RODBC)
library(sandwich)
library(lmtest)

con <- dbConnect(odbc(),
                 Driver='Devart ODBC Driver for PostgreSQL',
                 # ^ use on local Windows development environment
                 # Driver='PostgreSQL',
                 # ^ Use on shinyapps.io deployment
                 Server='18.204.57.173',
                 Port='5432',
                 Database='postgres',
                 Uid='postgres',
                 Pwd='&j>n!_nL]k&wWdE>*TVds4P6')


#Query is parametrized to line and start and end date
query1 <- as.character('SELECT * FROM \"public\".\"panel_zipcode\"')

dataA <- dbGetQuery(con, query1)

dataA$zipCodeYear <- paste0(dataA$zipcode,"_",dataA$year)

#Query is parametrized to line and start and end date
query2 <- as.character('SELECT * FROM \"public\".\"panel_microclimate\"')

dataB <- dbGetQuery(con, query2)

dataB$zipCodeYear <- paste0(dataB$zipcode,"_",dataB$year)

dataB <- dataB %>%
  select(5:11)

data <- left_join(dataA,dataB,by='zipCodeYear')

# data <- subset(data, subset = year >= 2016)

rm(dataA,dataB)

data$zipCodeYear <- as.factor(data$zipCodeYear)

data <- subset(data, subset = zipcode != 90802)

data[,8:14] <- data[,8:14]/data$polygon_area

plotThis <- function(data,type,variableA,variableB) {
  
  year <- 'year'
  
  if (type == 'scatter') {
    
    data%>%
      ggplot(aes_string(x = variableA, y=variableB, color = year)) + 
      geom_point(size = 0.1) + 
      geom_smooth(method = 'lm') + 
      theme(text = element_text(size = 8))
    
  } else if (type == 'boxplot') {
    
    data%>%
      ggplot(aes_string(y=variableA, x = year, fill = year, color = year)) + 
      geom_violin(alpha = 0.3) + 
      geom_boxplot(alpha = 0)  + 
      theme(text = element_text(size = 8))
    
  } else if (type == 'normality') {
    
    data%>%
      ggplot(aes_string(sample = variableA)) + stat_qq() + stat_qq_line() + theme_bw() +
      labs(y = paste0(variableA, 'Sample Quantiles'), x = 'Normal Theoretical Quantiles') + 
      theme(text = element_text(size = 8))
    
  }
  
}

data$vegetation <- data$lawn_area + data$tree_area

data$impervious <- data$impervious_area + data$soil_area + data$turf_area

#Eliminate observations with zero vegetation
data <- subset(data, subset = vegetation > 0)

#FILTER WEIRD YEARS
# data <- subset(data, subset = year > 2012)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA <- function(varName) {
  
  layout <- G / (A + B)
  
    layout +
    plot_annotation(
      # title = paste0(varName, " Class Land Coverage Statistics"),
      # theme = theme(plot.title = element_text(size = 10, hjust = 0.3, face = "bold"))
    )
}

plotLayoutB <- function(varName) {
  
  layout2 <- (D + E) / C 
  
  layout2 + 
    plot_annotation(
      caption = "Google Earth: Random Forest Model"
    )
  
}

```

# Aggregate Vegetation Area (Trees + Lawn)

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###VEGETATION AREA
A <- plotThis(data,'scatter','vegetation','lst_night_mean')
B <- plotThis(data,'scatter','vegetation','lst_day_mean')
C <- plotThis(data,'boxplot','vegetation')
D <- plotThis(data,'normality','vegetation')
E <- plotThis(data,'normality','log(vegetation)')

G <- ggplot(data = data, aes(x=vegetation)) + 
  geom_histogram(color='#086f69',fill='#086f69', alpha = 0.2) +
  labs(title = 'Vegetation') +
  theme_bw() 

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Vegetation')

plotLayoutB('Vegetation')

```

# Aggregate Impervious Area (Soil + Turf + Impervious)

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###IMPERVIOUS AREA
A <- plotThis(data,'scatter','impervious','lst_night_mean')
B <- plotThis(data,'scatter','impervious','lst_day_mean')
C <- plotThis(data,'boxplot','impervious')
D <- plotThis(data,'normality','impervious')
E <- plotThis(data,'normality','log(impervious)')

G <- ggplot(data = data, aes(x=impervious)) + 
  geom_histogram(color='#7c807c',fill='#7c807c', alpha = 0.2) +
  labs(title = 'Impervious') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Impervious')

plotLayoutB('Impervious')

```

# Impervious Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###LAWN_AREA AREA
A <- plotThis(data,'scatter','impervious_area','lst_night_mean')
B <- plotThis(data,'scatter','impervious_area','lst_day_mean')
C <- plotThis(data,'boxplot','impervious_area')
D <- plotThis(data,'normality','impervious_area')
E <- plotThis(data,'normality','log(impervious_area)')

G <- ggplot(data = data, aes(x=log(impervious_area))) + 
  geom_histogram(color='#7c807c',fill='#7c807c', alpha = 0.2) +
  labs(title = 'impervious_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Impervious Area')

plotLayoutB('Impervious Area')

```

# Lawn Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###LAWN_AREA AREA
A <- plotThis(data,'scatter','lawn_area','lst_night_mean')
B <- plotThis(data,'scatter','lawn_area','lst_day_mean')
C <- plotThis(data,'boxplot','lawn_area')
D <- plotThis(data,'normality','lawn_area')
E <- plotThis(data,'normality','log(lawn_area)')

G <- ggplot(data = data, aes(x=lawn_area)) + 
  geom_histogram(color='#1dd12d',fill='#1dd12d', alpha = 0.2) +
  labs(title = 'lawn_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Lawn Area')

plotLayoutB('Lawn Area')

```

# Tree Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TREE_AREA AREA
A <- plotThis(data,'scatter','tree_area','lst_night_mean')
B <- plotThis(data,'scatter','tree_area','lst_day_mean')
C <- plotThis(data,'boxplot','tree_area')
D <- plotThis(data,'normality','tree_area')
E <- plotThis(data,'normality','log(tree_area)')

G <- ggplot(data = data, aes(x=tree_area)) + 
  geom_histogram(color='#086f69',fill='#086f69', alpha = 0.2) +
  labs(title = 'tree_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Tree Area')

plotLayoutB('Tree Area')

```

# Water Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###LAWN_AREA AREA
A <- plotThis(data,'scatter','log(water_area)','lst_night_mean')
B <- plotThis(data,'scatter','log(water_area)','lst_day_mean')
C <- plotThis(data,'boxplot','log(water_area)')
D <- plotThis(data,'normality','water_area')
E <- plotThis(data,'normality','log(water_area)')

G <- ggplot(data = data, aes(x=log(water_area))) + 
  geom_histogram(color='#2252ff',fill='#2252ff', alpha = 0.2) +
  labs(title = 'water_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Water Area')

plotLayoutB('Water Area')

```

# Soil Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###LAWN_AREA AREA
A <- plotThis(data,'scatter','soil_area','lst_night_mean')
B <- plotThis(data,'scatter','soil_area','lst_day_mean')
C <- plotThis(data,'boxplot','soil_area')
D <- plotThis(data,'normality','soil_area')
E <- plotThis(data,'normality','log(soil_area)')

G <- ggplot(data = data, aes(x=log(soil_area))) + 
  geom_histogram(color='#a47041',fill='#a47041', alpha = 0.2) +
  labs(title = 'soil_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Soil Area')

plotLayoutB('Soil Area')

```

# Turf Area

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','log(turf_area)','lst_night_mean')
B <- plotThis(data,'scatter','log(turf_area)','lst_day_mean')
C <- plotThis(data,'boxplot','log(turf_area)')
D <- plotThis(data,'normality','turf_area')
E <- plotThis(data,'normality','log(turf_area)')

G <- ggplot(data = data, aes(x=log(turf_area))) + 
  geom_histogram(color='#0b9ed5',fill='#0b9ed5', alpha = 0.2) +
  labs(title = 'turf_area') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Turf Area')

plotLayoutB('Turf Area')

```

# Tree NDVI Mean

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','tree_ndvi_mean','lst_night_mean')
B <- plotThis(data,'scatter','tree_ndvi_mean','lst_day_mean')
C <- plotThis(data,'boxplot','tree_ndvi_mean')
D <- plotThis(data,'normality','tree_ndvi_mean')
E <- plotThis(data,'normality','log(tree_ndvi_mean)')

G <- ggplot(data = data, aes(x=log(tree_ndvi_mean))) + 
  geom_histogram(color='#086f69',fill='#086f69', alpha = 0.2) +
  labs(title = 'tree_ndvi_mean') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Tree NDVI Mean')

plotLayoutB('Tree NDVI Mean')

```

# Tree NDVI Min

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','tree_ndvi_min','lst_night_mean')
B <- plotThis(data,'scatter','tree_ndvi_min','lst_day_mean')
C <- plotThis(data,'boxplot','tree_ndvi_min')
D <- plotThis(data,'normality','tree_ndvi_min')
E <- plotThis(data,'normality','log(tree_ndvi_min)')

G <- ggplot(data = data, aes(x=log(tree_ndvi_min))) + 
  geom_histogram(color='#086f69',fill='#086f69', alpha = 0.2) +
  labs(title = 'tree_ndvi_min') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Tree NDVI Min')

plotLayoutB('Tree NDVI Min')

```

# Tree NDVI Max

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','tree_ndvi_max','lst_night_mean')
B <- plotThis(data,'scatter','tree_ndvi_max','lst_day_mean')
C <- plotThis(data,'boxplot','tree_ndvi_max')
D <- plotThis(data,'normality','tree_ndvi_max')
E <- plotThis(data,'normality','log(tree_ndvi_max)')

G <- ggplot(data = data, aes(x=log(tree_ndvi_max))) + 
  geom_histogram(color='#086f69',fill='#086f69', alpha = 0.2) +
  labs(title = 'tree_ndvi_max') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Tree NDVI Max')

plotLayoutB('Tree NDVI Max')

```

# Lawn NDVI Mean

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','grass_ndvi_mean','lst_night_mean')
B <- plotThis(data,'scatter','grass_ndvi_mean','lst_day_mean')
C <- plotThis(data,'boxplot','grass_ndvi_mean')
D <- plotThis(data,'normality','grass_ndvi_mean')
E <- plotThis(data,'normality','log(grass_ndvi_mean)')

G <- ggplot(data = data, aes(x=log(grass_ndvi_mean))) + 
  geom_histogram(color='#1dd12d',fill='#1dd12d', alpha = 0.2) +
  labs(title = 'grass_ndvi_mean') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Grass NDVI Mean')

plotLayoutB('Grass NDVI Mean')

```

# Lawn NDVI Min

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','grass_ndvi_min','lst_night_mean')
B <- plotThis(data,'scatter','grass_ndvi_min','lst_day_mean')
C <- plotThis(data,'boxplot','grass_ndvi_min')
D <- plotThis(data,'normality','grass_ndvi_min')
E <- plotThis(data,'normality','log(grass_ndvi_min)')

G <- ggplot(data = data, aes(x=log(grass_ndvi_min))) + 
  geom_histogram(color='#1dd12d',fill='#1dd12d', alpha = 0.2) +
  labs(title = 'grass_ndvi_min') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Grass NDVI Min')

plotLayoutB('Grass NDVI Min')

```

# Lawn NDVI Max

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','grass_ndvi_max','lst_night_mean')
B <- plotThis(data,'scatter','grass_ndvi_max','lst_day_mean')
C <- plotThis(data,'boxplot','grass_ndvi_max')
D <- plotThis(data,'normality','grass_ndvi_max')
E <- plotThis(data,'normality','log(grass_ndvi_max)')

G <- ggplot(data = data, aes(x=log(grass_ndvi_max))) + 
  geom_histogram(color='#1dd12d',fill='#1dd12d', alpha = 0.2) +
  labs(title = 'grass_ndvi_max') +
  theme_bw() 

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotLayoutA('Grass NDVI Max')

plotLayoutB('Grass NDVI Max')

```

# Mean Temperature

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###TURF_AREA AREA
A <- plotThis(data,'scatter','lst_day_mean','lst_night_mean')

B <- plotThis(data,'boxplot','lst_day_mean')
C <- plotThis(data,'boxplot','lst_night_mean')

D <- ggplot(data = data, aes(x=lst_day_mean)) + 
  geom_histogram(color='orange',fill='orange', alpha = 0.2) +
  labs(title = 'lst_day_mean') +
  theme_bw() 

E <- ggplot(data = data, aes(x=lst_night_mean)) + 
  geom_histogram(color='darkblue',fill='darkblue', alpha = 0.2) +
  labs(title = 'lst_night_mean') +
  theme_bw() 

layout1 <- A / (B + C)

layout2 <- D / E

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

layout1

layout2 + 
    plot_annotation(
      caption = "Google Earth: Random Forest Model"
    )

```

# Create MicroClimate Panel Data Set

```{r}

data <- subset(data, subset = year > 2012)

# Create panel dataframe object
microClimatePanel <- pdata.frame(data, index=c("zipcode", "year"))

```

# First Attempt with Traditional OLS Model

```{r, results='asis'}

OLSM1 <- lm(
  log(lst_day_mean) ~ 0 + factor(year) + polygon_area + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  data = microClimatePanel)

OLSM2 <- lm(
  log(lst_night_mean) ~ 0 + factor(year) + polygon_area + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  data = microClimatePanel)

stargazer::stargazer(OLSM1,OLSM2, single.row = TRUE, 
                     title = 'OLS Model',
                     column.labels = c("OLSModel Day Temp",
                                       "OLSModel Night Temp"))

```

# Second Attempt with a Mixed Effects Model

```{r, results='asis'}

feM1 <- plm(
  log(lst_day_mean) ~ 0 + factor(year) + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  index = c(zipcode, year), data = microClimatePanel, model = 'within')

feM2 <- plm(
  log(lst_night_mean) ~ 0 + factor(year) + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  index = c(zipcode, year), data = microClimatePanel, model = 'within')

stargazer::stargazer(feM1,feM2, single.row = TRUE, 
                     title = 'Fixed Effects Model',
                     column.labels = c("FixedEffects Day Temp",
                                       "FixedEffects Night Temp"))

```

# Compare Performance of OLS vs Mixed Effects Models

```{r}

pFtest(feM1, OLSM1) 
## Fixed effects is a better choice than OLS

```

## Fixed Effects is a Better Choice, Discard OLS Model

# Try a Random Effects Model

```{r, results='asis'}

reM1 <- plm(
  log(lst_day_mean) ~ 0 + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  index = c(zipcode, year), data = microClimatePanel, model = 'random')

reM2 <- plm(
  log(lst_night_mean) ~ 0 + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  index = c(zipcode, year), data = microClimatePanel, model = 'random')

stargazer::stargazer(reM1,reM2, 
                     single.row = TRUE, 
                     title = 'Random Effects Model', 
                     column.labels = c("RandomEffects Day Temp",
                                       "RandomEffects Night Temp"))

```

# Compare Performance of Mixed Effects vs Random Effects Models

```{r}

phtest(feM1, reM1)
## the p-value is significant so we choose fixed effects
## (since the unique errors are correlated with the regressors).

```

## the p-value is significant so we choose fixed effects (since the unique errors are correlated with the regressors). There is omitted variable bias at the higher level that the RE model has not accounted for (but the FE model has).

# Try a Fixed Effects Model with Fixed Time

```{r, results='asis'}

feM2FixedTime <- plm(
  log(lst_day_mean) ~ 0 + tree_area + lawn_area + water_area + soil_area +
    turf_area + grass_ndvi_mean + tree_ndvi_mean,
  index = c(zipcode, year), data = microClimatePanel, model = 'within')

stargazer::stargazer(feM2FixedTime, single.row = TRUE)

```

```{r}

pFtest(feM1,feM2FixedTime)

```

```{r}

plmtest(feM1, effect="time", type="bp")

```

```{r}
pbgtest(feM1)

```

```{r}

coeftest(feM1, vcovHC) 

```

```{r}

coeftest(feM1, vcovHC(feM1, method = "arellano")) 
t(sapply(c("HC0", "HC1", "HC2", "HC3", "HC4"), function(x) sqrt(diag(vcovHC(feM1, method = "arellano", type = x)))))

```

```{r}

totalRobust <- coeftest(feM1, vcov = vcovHC(feM1, type = 'HC0'))
cInterval <- coefci(feM1, vcov. = vcovHC(feM1, type = 'HC0'))

```

```{r}

print(totalRobust)

```

```{r}

print(cInterval)

```

```{r, results='asis'}

stargazer::stargazer(OLSM1,feM1,reM1,feM2FixedTime, 
                     font.size = 'tiny',
                     title = 'Regression Models Sumamry',
                     column.labels = c("OLS", "FixedEffects",
                                       "RandomEffects",
                                       "FixedEffectsFixedTime"))

```

```{r}

qqnorm(residuals(feM1), ylab = 'Residuals')
qqline(residuals(feM1))

```

```{r}

hist(residuals(feM1), xlab = 'Residuals')

```


